Alien species

### 2023-09-28 alien_species.Rmd
Reasoning for calculating HIA-values at municipality level #82
Investiagte how the R7 scale is used and fix figure text #81

```{r fremmedart-prosentVSinnslag, fig.cap="Comparing the R7 scale (x axis) which is used in the nature type monitoring program with percentage cover (y-axis), which is how alien species is recorded in ANO. I am assuming the x axis is shifted downwards compared to the original R7 scale which range from 1 to 7, so that a value of 0 here equals an R7 value of 1. Cropped from Evju et al (2022)."}
knitr::include_graphics("images/fremmedart_prosentVSinnslag.PNG")
```

@@

I also want to split these four HIA classes based on municipality. To do
this I need the two layers to have the same CRS.

>>>>

```{r fremmedart-prosentVSinnslag, fig.cap="Comparing the R7 scale (x axis) which is used in the nature type monitoring program with percentage cover (y-axis), which is how alien species is recorded in GRUK. I am assuming the x axis is shifted downwards compared to the original R7 scale which range from 1 to 7, so that a value of 0 here equals an R7 value of 1. Note also that this relationship is based on limited data from just one nature type and in smaller diameter circles than the other data we use in this indicator. Cropped from Evju et al (2022)."}
knitr::include_graphics("images/fremmedart_prosentVSinnslag.PNG")
```

@@

I also want to split these four HIA classes based on municipality. 
For a [related indicator](#HIA-slitasje) I used combinations of HIA and region, but for alien species I think
that there is too much variation also inside each region (esp north-south) so that we need a finer division of strata.
To do this I need the two layers to have the same CRS.
